%------------------------------------------------------------------------------
% CV in Latex
% Author : Charles Rambo
% Based off of: https://github.com/sb2nov/resume and Jake's Resume on Overleaf
% Most recently updated version may be found at https://github.com/fizixmastr 
% License : MIT
%------------------------------------------------------------------------------

\documentclass[A4,11pt]{article}
%\documentclass[letterpaper,14pt]{article} %For use in US
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{tikz}
\usepackage[super]{nth}
\input{glyphtounicode}

\begin{comment}
I am by no means a professional when it comes to the CV's/resumes, I have
received various trainings on how to write a CV and resume from my high 
school, as well as the Austin College and University of Eastern Finland's
career counseling departments. As I intend to share my CV as a template, I 
feel that it is my responsibility to provide explanations of my work.
\end{comment}


%-----FONT OPTIONS-------------------------------------------------------------
\begin{comment}
The font of the document will impact not just how readable it is, but how it is
perceived. In the "The Craft of Scientific Writing" by Michael Alley, shares a
common fonts for publication as well as their use. I have chosen to use
Palatino for its legibility, some others are given below. There is far too much
about typography to discus here. Note: serif fonts have short projecting
strokes, sans-serif fonts are sans (without) these strokes.
\end{comment}


% serif
 \usepackage{palatino}
% \usepackage{times} %This is the default as well
% \usepackage{charter}

% sans-serif
% \usepackage{helvet}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

%-----PAGE SETUP---------------------------------------------------------------

% Adjust margins
\addtolength{\oddsidemargin}{-1cm}
\addtolength{\evensidemargin}{-1cm}
\addtolength{\textwidth}{2cm}
\addtolength{\topmargin}{-1cm}
\addtolength{\textheight}{2cm}

% Margins for US Letter size
%\addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\evensidemargin}{-0.5in}
%\addtolength{\textwidth}{1in}
%\addtolength{\topmargin}{-.5in}
%\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0cm}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that .pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-----CUSTOM COMMANDS FOR FORMATTING SECTIONS----------------------------------
\newcommand{\CVItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\CVSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small#3 & \small #4 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\CVSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \text{\small#1} & \text{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\CVSubItem}[1]{\CVItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\CVSubHeadingListStart}{\begin{itemize}[leftmargin=0.5cm, label={}]}
% \newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]} % Uncomment for US
\newcommand{\CVSubHeadingListEnd}{\end{itemize}}
\newcommand{\CVItemListStart}{\begin{itemize}}
\newcommand{\CVItemListEnd}{\end{itemize}\vspace{-5pt}}

%------------------------------------------------------------------------------
% CV STARTS HERE  %
%------------------------------------------------------------------------------
\begin{document}

%-----HEADING------------------------------------------------------------------
% Without picture
\begin{center}
  \textbf{\LARGE \scshape Cedric P.-E. MANOUAN} \\ \vspace{1pt} %\scshape sets small capital letters, remove if desired
  \small{\textbf{Contact : }+250 (0) 791 591 607} $|$
  \href{mailto:cmanouan@alumni.cmu.edu}{\textbf{Email:} cmanouan@alumni.cmu.edu} $|$ \\
  % Be sure to use a professional *personal* email address
  \href{https://www.linkedin.com/in/cpem/} {\textbf{Linkedin:} Cédric pascal-emmanuel MANOUAN} $|$ 
  % you should adjust you linked in profile name to be professional and recognizable
  \href{https://github.com/dric2018/}{\textbf{Github:} dric2018}\\

\end{center}

%-----Summary----------------------------------------------------------------
\section{Summary}

Software/Machine learning engineer with a focus on deep learning for over 3 years. \\%Hard-worker with the ability to work independently and with a good team spirit. \\
Experience in deep learning projects for Natural Language Processing and Computer Vision: end-to-end development from data preparation/exploration to model definition and optimization.
\\Ability to evolve and work efficiently in a collaborative environment. %(even remotely).


%-----EDUCATION----------------------------------------------------------------
\section{Education}
\CVSubHeadingListStart
%    \CVSubheading % Example
%      {Degree Achieved}{Years of Study}
%      {Institution of Study}{Where it is located}
\CVSubheading
{{Master of Science $|$ \emph{\small{Information Technology - Applied Machine Learning}}}}{August 2021 -- May 2023}
{Carnegie Mellon University}{Kigali, Rwanda}
\CVSubheading
{{Master of Science (Semester 7) $|$ \emph{\small{Information Systems and Software engineering}}}}{October 2019 -- March 2020}
{Ecole Supérieure Africaine des TIC (ESATIC) }{Abidjan, Côte d'Ivoire}
\CVSubheading
{Bachelor of Science $|$ \emph{\small{Systems, Computer Networks and Telecommunications}}}{October 2016 -- September 2019}
{Ecole Supérieure Africaine des TIC (ESATIC) - \href{https://drive.google.com/file/d/1AHcLovrqVw6Awh7r_sUYj2X1VdPfAZGq/view?usp=sharing}{See degree certificate here}}{Abidjan, Côte d'Ivoire}
\CVSubHeadingListEnd

%-----WORK EXPERIENCE----------------------------------------------------------
\begin{comment}
try to briefly explain what you did and why it is relevant to the position you
are seeking
\end{comment}

\section{Work Experience}
\CVSubHeadingListStart
%    \CVSubheading %Example
%      {What you did}{When you worked there}
%      {Who you worked for}{Where they are located}
%      \CVItemListStart
%        \CVItem{Why it is important to this employer}
%      \CVItemListEnd
\CVSubheading
{Research Associate }{Summer 2023}
{Carnegie Mellon University}{Kigali, Rwanda}
\CVItemListStart
\CVItem{Assisting Prof. David Vernon with the realization of the Situation Model Framework in \\
the CRAM Cognitive Architecture using a Joint Episodic-Procedural-Semantic (JEPS) \\
Associative Memory.}
\CVItemListEnd

\CVSubheading
{Graduate Research and Teaching Assistant }{Fall 2022 - Spring 2023}
{Carnegie Mellon University}{Kigali, Rwanda}
\CVItemListStart
\CVItem{Assisting Prof. Bhiksha Raj in 11785 - Introduction to Deep Learning: \\Natural Language \& Audio Processing}
\begin{itemize}
  \item Prepared and Co-Lead the \textit{Language Modeling} homework assignment in Fall 2022
\end{itemize}
\CVItem{Assisting Prof. Moise Busogi in Machine Learning for Earth Observation (ML4EO)}
\CVItem{Research in Machine Learning for Earth Observation supervised by Dr. Moise Busogi}
\CVItemListEnd

% \CVSubheading
% {Data science Intern}{Fall 2022}
% {TIR}{Abidjan, Cote d’Ivoire}
% \CVItemListStart
% \CVItem{Implemented a Transformer-based OCR model line items extraction}
% \CVItem{Developed an API that leverages the OCR for medical prescriptions \\ and general documents processing}
% \CVItemListEnd

\CVSubheading
{Software engineering/Data science Intern }{May 2021 -- July 2021}
{Zindi}{Remote}
\CVItemListStart
\CVItem{Data science competitions preparation}
\CVItemListEnd

\CVSubheading
{Developer Intern (BSc. end project)}{April 2019 -- June 2019}
{Project of Digital Solutions for the opening up of Rural Areas and E-Agriculture (PSNDEA)}{Abidjan, Côte d'Ivoire}
\CVItemListStart
\CVItem{Built an Internet of Things (IoT) system for data acquisition in a cassava field}
\CVItem{Developed a REST CRUD API based on NodeJs and MySQL to store data from both \\sensors and farmers inputs}
\CVItem{Developed a regression model to predict the yield of a given cassava field based on \\real-time and stored data}
\CVItem{Deployed the machine leaning model to an edge device (Raspbery Pi 3) using tensorflowJS}
\CVItemListEnd

\CVSubHeadingListEnd

%-----SKILLS-------------------------------------------------------------------
\begin{comment}
This section is compressed from the various skills sections that Euro CV
recommends.
\end{comment}

\section{Skills}
\begin{itemize}[leftmargin=0.5cm, label={}]
  \small{\item{
        \textbf{Languages}{: French (Native), English (Bilingual, Professional)} \\
        \textbf{Programming}{:
          \begin{itemize}
            \item Python \\
                  \begin{itemize}
                    \item Data manipulation and visualization: Pandas, Plotly, Matplotlib, Seaborn
                    \item Machine: NumPy, Scikit-learn, Lightgbm, Xgboost, Streamlit
                    \item Deep learning: PyTorch, Transformers, Tensorflow/Keras
                    \item API development: Flask, FastAPI
                  \end{itemize}
            \item C++
              \begin{itemize}
                \item Data structures and Algorithms
              \end{itemize}
            % \item Bash/task automation

            % \item JavaScript
            %       \begin{itemize}
            %         \item Backend development with NodeJS
            %       \end{itemize}
            % \item HTML/CSS/web development (\textbf{intermediate})

          \end{itemize}

        }
        % \textbf{Document Creation}{: Microsoft Office, LaTeX, Markdown} \\
        % \textbf{Cloud computing / Code management / DevOps}{: Git, Docker, Amazon Web Services (EC2/ECS)} \\
        % \textbf{Operating Systems}{: Ubuntu, Mac OS} \\
        }}
\end{itemize}

%-----PROJECTS AND RESEARCH----------------------------------------------------
\begin{comment}
Ideally the title of the work should speak for what it is. However if you feel
like you should explain more about why the project is applicable to this job,
use item list as is shown in the work experience section.
\end{comment}

\section{Projects and Research}
\CVSubHeadingListStart
%    \CVSubheading
%      {Title of Work}{When it was done}
%      {Institution you worked with}{unused}
\CVSubheading
{{Course project - Recommender Systems} $|$ \emph{\small{CMU-Africa}}}{Fall 2022}
{Developed a Content-Based Recommender system for scientific papers as part of my mini project \\
in 04800-B Intro to Recommender Systems at Carnegie Mellon university-Africa.\\
  \textbf{Project link} : \href{https://github.com/dric2018/ScietificPaperCBRS}{CBRS for scientific papers}
}{}

\CVSubheading
{{Data science competition - Image classification} $|$ \emph{\small{ZINDI}}}{Fall 2020}
{Developed a machine learning model to classify Tuberculosis and Normal X-Ray images \\
  for an educational purpose. \\
  \textbf{Ranking} : \nth{7}/104, \textbf{\href{https://zindi.africa/competitions/runmila-ai-institute-minohealth-ai-labs-tuberculosis-classification-via-x-rays-challenge/leaderboard}{Click and look for team DataLabCI on the leaderboard}} \\
  \textbf{Project link} : \href{https://github.com/dric2018/ZindiTuberculosisClassification}{Tuberculosis X-Rays classification}
}{}


\CVSubheading
{{Data science competition - Audio classification} $|$ \emph{\small{ZINDI}}}{Fall 2020}
{Contributed to the development of a machine learning model to classify audio utterances \\
  in Luganda and English from Uganda. \\
  \textbf{Ranking} : \nth{7}/255, \textbf{\href{https://zindi.africa/competitions/giz-nlp-agricultural-keyword-spotter/leaderboard}{Click and look for team wakanda on the leaderboard}} \\
  \textbf{Project link} : \href{https://github.com/NazarioR9/GIZ-NLP-Agricultural-Keyword-Spotter}{GIZ-NLP-Agricultural-Keyword-Spotter}
}{}

\CVSubheading
{{Data science hackathon - Image classification} $|$ \emph{\small{ZINDI}}}{Fall 2020}
{Contribued to the development of a machine learning model to identify whether a person in an image \\
  is wearing a face mask or not. \\
  \textbf{Ranking} : \nth{3}, \textbf{ \href{https://zindi.africa/competitions/spot-the-mask-challenge}{Click and look for team TheCIA on the leadernoard}} \\
  \textbf{Project link} : \href{https://github.com/NazarioR9/Spot-the-Mask-challenge-3rd-Place}{Face mask classification}
}{}

\CVSubheading
{{\nth{1} prize Hackathon Level 2 (48h) - Image recognition} $|$ \emph{\small{ESATIC}}}{May 2018}
{Contributed to the development of a deep learning model to recognize West African \\
bank notes and coins.

}{}

\CVSubheading
{{\nth{1} prize Hackathon Level 1 (24h) - Cryptography} $|$ \emph{\small{ESATIC}}}{May 2017}
{Contributed to research and writing (in C++) the encryption algorithm behind an executable program.

}{}

\CVSubHeadingListEnd

%-----CONFERENCES AND PRESENTATIONS--------------------------------------------
\begin{comment}
Again the title should have already been enough, but if it is necessary to add
descriptions maintain the consistency from prior sections
\end{comment}

%\section{Conferences and Presentations}
%\CVSubHeadingListStart
%    \CVSubheading % Example
%      {Work Presented}{When}
%      {Occasion}{}
%\CVSubheading
%{Photometric Filter Fidelity and Use for Be Star Identification}{November 2017}
%{Austin College Physics Research Seminar}{}
%\CVSubheading
%{Reflectometry for Volumetric Soil Moisture Measurement}{May 2017}
%{Austin College Atmospheric Physics Fair}{}
%\CVSubheading
%{Design and Manufacturing of Products using 3D Printing}{April 2017}
%{Austin College Student Scholarship Conference}{}
%\CVSubHeadingListEnd

% %-----HONORS AND AWARDS--------------------------------------------------------
% \section{Honors and Awards}
% \CVSubHeadingListStart
% %    \CVSubheading %Example
% %      {What}{When}
% %      {Short Description}{}

% \CVSubheading
% {Master Card Foundation Scholarship}{2021 -- 2023}
% {Merit based scholarship to support international study experiences (at Carnegie Mellon University)}{}

% \CVSubHeadingListEnd

%-----TEACHING EXPERIENCE------------------------------------------------------
\begin{comment}
Section is here as it applied to my application for positions in academia.
Remember to tailor the resume for to the position.
\end{comment}

%\section{Teaching Experience}
%\CVSubHeadingListStart
%    \CVSubheading
%      {What}{When}
%      {School}{Where}
%\CVSubheading
%{High School Physics (11 Weeks Teaching/Observing)}{Fall 2017}
%{Denison High School}{Denison, TX}
%\CVSubheading
%{High School Calculus (11 Weeks Teaching/Observing)}{Fall 2017}
%{Denison High School}{Denison, TX}
%\CVSubheading
%{High School Geometry (9 Weeks Teaching/Observing)}{Spring 2016}
%{Sherman High School}{Sherman, TX}
%\CVSubHeadingListEnd

%-----COMMUNITY INVOLVEMENT----------------------------------------------------
\section{Interests \& Community Involvement}
\CVSubHeadingListStart
%    \CVSubheading %Example
%      {What you did}{When you worked there}
%      {Who you worked for}{Where they are located}
\CVSubheading
{NLP and Robotics}{Spring 2023}
{Joint Episodic-Procedural-Semantic Associative Memory (JEPSAM)}{Rwanda, Kigali, CMU-Africa}
\CVItemListStart
\CVItem{Since Spring 2023, I have been contributing to the JEPSAM project. \\
This project aims to provide an implementation of the Situation Model \\ 
Framework for the Cognitive Robot Abstract Machine (CRAM).
% The main objective of the JEPSAM project is to design and develop a system that can \\
% help robots perform everyday tasks in a flexible and adaptive manner, \\“similar to how humans do”. \\
% This will be achieved by using the CRAM architecture, which combines \\
% several cognitive processes, including perception, reasoning, planning, and execution.
}
\CVItemListEnd

\CVSubheading
{Data Science Club}{December 2021 -- November 2022}
{Lead and coordinator}{Rwanda, Kigali, CMU-Africa}
\CVItemListStart
\CVItem{Participants recruitment for Zindi UMOJAHACK 2022 (enrolled 30+ new users)}
\CVItemListEnd

\CVSubheading
{Data Science Côte D'Ivoire}{2020 -- Present}
{Free tutoring for local students/AI enthusiasts }{Côte d'Ivoire, remote}

\CVSubheading
{Zindi University ambassador}{June 2020 -- July 2021}
{}{Côte d'Ivoire, remote}
\CVItemListStart
\CVItem{Participating in competitions and hackathons on the platform (username : \href{https://zindi.africa/users/\_MUFASA\_/}{\textbf{\_MUFASA\_}})}%, Top 100 among zindi data scientists}
\CVItem{Co-lead of the platform development group (improvements and new ideas)}
\CVItem{Participants recruitment for UMOJAHACK 2021 (enrolled 15+ new users)}
\CVItemListEnd

\CVSubheading
{Co-founder of the Internet of Things and Artificial Intelligence club}{2019}
{ESATIC}{Abidjan, Côte d'Ivoire}
\CVSubHeadingListEnd

% \section{Other qualities}
% \CVItemListStart
% \CVItem{Motivator \& Leader}
% \CVItem{Initiative taker}
% \CVItem{Problems solver}
% \CVItemListEnd
%------------------------------------------------------------------------------
\end{document}